---
title: "GSA well failure"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    orientation: rows
    navbar:
      - { title: "Instructions",  align: right}
      - { title: "About", href: "https://google.com", align: right}
      - { icon: "fa-github", href: "https://google.com", align: right}
    css: etc/w3.css
    self_contained: false
    #logo: etc/cwq_8_pixels.png
    #favicon: etc/cwq_8_pixels.png
---

<!-- a wee bit of JS that allows a modal popup when the first -->
<!-- list element of the navbar (Instructions) is clicked -->
<!-- adapted from: https://github.com/rstudio/flexdashboard/issues/208 -->
<script>
$('.navbar-brand').wrap('<a href="http://www.google.com">');

$(document).ready(function() {
  $('#dashboard-container').on('flexdashboard:layoutcomplete', 
    function() {
      $('#navbar li:nth-child(1)').click(function() {
        $('#md-instructions').modal(); });
  })
})

<!-- modal popup when valueboxes are clicked -->
$(document).ready(function() {
  $('#dashboard-container').on('flexdashboard:layoutcomplete', 
    function() {
      $('#groundwater-level-decline').click(function() {
        $('#md-groundwater-level-decline').modal(); });
  })
})

<!-- modal popup when valueboxes are clicked -->
$(document).ready(function() {
  $('#dashboard-container').on('flexdashboard:layoutcomplete', 
    function() {
      $('#well-failures').click(function() {
        $('#md-well-failures').modal(); });
  })
})

<!-- modal popup when valueboxes are clicked -->
$(document).ready(function() {
  $('#dashboard-container').on('flexdashboard:layoutcomplete', 
    function() {
      $('#percent-of-failing-wells').click(function() {
        $('#md-percent-of-failing-wells').modal(); });
  })
})

<!-- modal popup when valueboxes are clicked -->
$(document).ready(function() {
  $('#dashboard-container').on('flexdashboard:layoutcomplete', 
    function() {
      $('#cost').click(function() {
        $('#md-cost').modal(); });
  })
})



</script>

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(bsplus)
library(leaflet)
library(htmltools)
library(htmlwidgets)
library(plotly)
library(stringr)
library(readr)
library(here)

# read groundwater level and gsas
gwl <- readr::read_rds(here::here("code", "results", "gwl_2019_avg_ll.rds"))
gsa <- readr::read_rds(here::here("code", "results", "gsa_ll.rds"))

source(here("jamstack", "etc", "functions.R"))

# if(params %in% )is_gsa_page = 
```

Row {.sidebar data-width=150 data-padding=10}
-----------------------------------------------------------------------


```{r sidebar downdown menus}
# GSA dropdown
tags$div(
  class="dropdown",
  tags$button(
    class="dropbtn", "GSA"),
  tags$div(
    class = "dropdown-content",
    tags$a(href = "https://www.gsawellfailure.com/ALL/mt", "ALL"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/northern-central/mt", "Northern Central (DM)"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/farmers/mt", "Farmers (DM)"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/east-kaweah/mt", "East Kaweah"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/chowchilla/mt", "Chowchilla"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/madera-joint/mt", "Madera Joint"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/central-kings/mt", "Central Kings"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/north-fork-kings/mt", "North Fork Kings"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/south-kings/mt", "South Kings"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/mc-mullin/mt", "Mc Mullin"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/gravelly-ford-madera/mt", "Gravelly Ford (Madera)"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/pixley-tule/mt", "Pixley (Tule)"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/westside/mt", "Westside"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/greater-kaweah/mt", "Greater Kaweah"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/new-stone-madera/mt", "New Stone (Madera)"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/mid-kaweah/mt", "Mid Kaweah"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/aliso/mt", "Aliso (DM)"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/merced/mt", "Merced"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/kings-river-east/mt", "Kings River East"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/north-kings/mt", "North Kings"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/henry-miller-kern/mt", "Henry Miller (Kern)"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/grassland/mt", "Grassland (DM)"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/tulare-lake/mt", "Tulare Lake"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/east-tule/mt", "East Tule"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/olcese-kern/mt", "Olcese (Kern)"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/root-creek-madera/mt", "Root Creek (Madera)"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/buena-vista-kern/mt", "Buena Vista (Kern)"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/kern-river/mt", "Kern River"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/delano-earlimart-tule/mt", "Delano-Earlimart (Tule)"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/sjrec/mt", "SJREC (DM)"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/fresno-county/mt", "Fresno County (DM)"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/james-kings/mt", "James (Kings)"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/kern-groundwater-authority/mt", "Kern Groundwater Authority"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/eastern-san-joaquin/mt", "Eastern San Joaquin"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/alpaugh-tule/mt", "Alpaugh (Tule)"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/lower-tule-river/mt", "Lower Tule River"),
    tags$a(href = "https://www.gsawellfailure.com/gsas/tri-county-tule/mt", "Tri-County (Tule)")
    )
)

tags$br()
tags$br()

# groundwater level dropdown
# if(is_gsa_page == TRUE){ evaluate }
tags$div(
  class="dropdown",
  tags$button(
    class="dropbtn", paste0("Groundwater scenario")),
  tags$div(
    class = "dropdown-content",
    tags$a(href = "https://www.richpauloo.com", "Minimum Threshold"),
    tags$a(href = "https://www.richpauloo.com", "0 ft decline"),
    tags$a(href = "https://www.richpauloo.com", "10 ft decline"),
    tags$a(href = "https://www.richpauloo.com", "20 ft decline"),
    tags$a(href = "https://www.richpauloo.com", "30 ft decline"),
    tags$a(href = "https://www.richpauloo.com", "40 ft decline"),
    tags$a(href = "https://www.richpauloo.com", "50 ft decline"),
    tags$a(href = "https://www.richpauloo.com", "100 ft decline"),
    tags$a(href = "https://www.richpauloo.com", "150 ft decline"),
    tags$a(href = "https://www.richpauloo.com", "200 ft decline"),
    tags$a(href = "https://www.richpauloo.com", "250 ft decline"),
    tags$a(href = "https://www.richpauloo.com", "300 ft decline"),
    tags$a(href = "https://www.richpauloo.com", "400 ft decline"),
    tags$a(href = "https://www.richpauloo.com", "500 ft decline")
    )
)
```


<!-- Row {data-width=100} -->
Row
-----------------------------------------------------------------------

```{r bs modal}
bs_modal(
  id = "md-instructions",
  title = "Using Markdown",
  body = includeMarkdown(system.file("markdown","modal.md",package="bsplus"))
)
bs_modal(
  id = "md-groundwater-level-decline",
  title = "Using Markdown",
  body = includeMarkdown(system.file("markdown","modal.md",package="bsplus"))
)
bs_modal(
  id = "md-well-failures",
  title = "Using Markdown",
  body = includeMarkdown(system.file("markdown","modal.md",package="bsplus"))
)
bs_modal(
  id = "md-percent-of-failing-wells",
  title = "Using Markdown",
  body = includeMarkdown(system.file("markdown","modal.md",package="bsplus"))
)
bs_modal(
  id = "md-cost",
  title = "Using Markdown",
  body = includeMarkdown(system.file("markdown","modal.md",package="bsplus"))
)
```

```{r bs modal 2, include=FALSE}
bs_button("Click for modal", button_type = "primary") %>%
  bs_attach_modal("md-instructions")
bs_button("Click for modal", button_type = "primary") %>%
  bs_attach_modal("md-groundwater-level-decline")
bs_button("Click for modal", button_type = "primary") %>%
  bs_attach_modal("md-well-failures")
bs_button("Click for modal", button_type = "primary") %>%
  bs_attach_modal("md-percent-of-failing-wells")
bs_button("Click for modal", button_type = "primary") %>%
  bs_attach_modal("md-cost")
```


### Groundwater level decline
```{r gwl decline}
valueBox("Min threshold",
         color = "primary",
         icon = "ion-arrow-down-a")
```

### Well failures
```{r count of well failures}
valueBox("5000-10000", color = "danger", icon = "fa-times-circle")
```

### Percent of failing wells
```{r well failure percent}
valueBox("15-60", color = "warning", icon = "fa-percent")
```

### Cost
```{r cost}
valueBox("$1.2-1.3M", color = "success", icon = "ion-cash")
```


Row
-----------------------------------------------------------------------

### GSAs and groundwater surfaces 
```{r, leaflet}
# color palettes for gwl decline
col <- rev(colormap::colormap(colormap::colormaps$magma, nshades = 20))
pal <- colorNumeric(col, raster::values(gwl), na.color = "transparent")

#pal2 <- colorNumeric(col, raster::values(gwl)/2, na.color = "transparent")
gwl2 <- gwl/2

gsa_names <- gsa@data$gsp_name %>% 
  tolower() %>% 
  str_remove_all("[\\(\\)]") %>% 
  str_remove_all(" dm") %>% 
  str_replace_all(" |-", "_") 

# read all plotly in for testing
l <- vector("list", length(gsa_names))
for(i in 1:length(gsa_names)){
  l[[i]] <- 
    read_rds(paste0("~/Github/aife/plotly/100_", gsa_names[i], ".rds")) %>% 
    as.tags() %>%
    {tags$div(style="width:270px; height:220px;", .)} %>%
    as.character() %>% 
    stringr::str_replace("height:400px","height:100%")
  l[[i]] <- 
    paste0("<em><b>", "GSA NAME", "</b></em><br>",
           "N-M wells fail at min threshold<br>",
           "$X-Y estimated cost<br>",
           l[[i]]
    )
}


# test
leaflet(gsa) %>% 
  
  # tiles
  addProviderTiles(providers$CartoDB,             group = "Light") %>% 
  
  # center
  setView(-119.7, 36.8, 7) %>% 
  
  # groundwater level
  addRasterImage(gwl, opacity = 0.8, colors = pal,
                 layerId = "2019", group = "2019 groundwater level") %>%
  addRasterImage(gwl2, opacity = 0.8, colors = pal,
                 layerId = "2040", group = "2040 min threshold") %>%
  addLegend(pal = pal, values = raster::values(gwl),
            title    = "Groundwater <br>level (ft. BLS)",
            position = "bottomright") %>%
  
  # raster value display
  leafem::addMouseCoordinates() %>%
  leafem::addImageQuery(gwl, type="mousemove", layerId = "2019",
                        group = "2019 groundwater level", prefix = "",
                        digits = 2, position = "bottomright") %>%
  leafem::addImageQuery(gwl2, type="mousemove", layerId = "2040",
                        group = "2040 min threshold", prefix = "",
                        digits = 2, position = "bottomright") %>%
  
  # layer control
  addLayersControl(
    overlayGroups = c("critical priority GSAs"),
    baseGroups    = c("2019 groundwater level", "2040 min threshold"),
    options       = layersControlOptions(collapsed = FALSE,
                                         position = "bottomleft")
  ) %>%
  
  # zoom to home
  addEasyButton(easyButton(
    icon="fa-globe", title="Zoom to Level 1",
    onClick=JS("function(btn, map){ map.setView([36.8, -119.7], 7); }"),
    position = "topleft")
  ) %>% 
  
  # polygons
  addPolygons(data = gsa, weight = 1, opacity = 1, fillOpacity = 0.1, 
              group = "critical priority GSAs",
              label = ~gsp_name, 
              highlightOptions = 
                highlightOptions(color = "black", weight = 2,
                                 bringToFront = TRUE),
              labelOptions = labelOptions(textsize = "13px"),               
              popup = l
  ) %>% 
  
  onRender(
    "function(el,x) {
    this.on('popupopen', function() {HTMLWidgets.staticRender(); remove()})
    }"
  ) %>%
  add_deps("plotly") %>%
  htmltools::attachDependencies(plotly:::plotlyMainBundle(), append = TRUE) %>%
  htmltools::attachDependencies(crosstalk::crosstalkLibs(),  append = TRUE) %>%
  browsable()
```

### Forecasted well failure rates
```{r, plot}
readr::read_rds("../plotly/10_ALL.rds")
```



