---
# title: '`r paste0("GSA well failure ", " /  ", params$gsa_names_full, "  /  ", params$decline_v_full)`'
title: "GSA Well Failure"
output: 
  flexdashboard::flex_dashboard:
    logo: ../../../etc/gwf_8_pixels.png
    favicon: ../../../etc/gwf_8_pixels.png
    vertical_layout: fill
    orientation: rows
    navbar:
      # - { title: "How to use this website",  align: left}
      # - { title: "Methodology", align: left}
      # - { title: "Data", align: left}
      # - { title: "About", align: left}
      #- { title: "Home", href: "#home", align: right }
      - { title: "Map", href: "#map", align: right }
      # - { title: "Instructions", href: "#instructions", align: right }
      - { title: "Methodology", href: "#methodology", align: right }
      - { title: "Data", href: "#data", align: right }
      - { icon: "fa-question-circle",  href: "#instructions", align: right}
      # - { title: "About", href: "#about", align: right }
      # - { icon: "fa-github", href: "https://www.github.com/richpauloo/aife", align: right}
    #css: /Users/richpauloo/Github/aife/jamstack/etc/w3.css
    #self_contained: false
    #lib_dir: libs
params: 
  selected_gsa:     "hold"
  selected_decline: "hold"
  gsa_names_full:   "hold"
  decline_v_full:   "hold"
---

<!-- code syntax highlighting, a la https://cdn.jsdelivr.net/gh/highlightjs/cdn-release@10.5.0/build/styles/ -->
<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/highlightjs/cdn-release@10.5.0/build/styles/stackoverflow-dark.min.css">
<script src="https://cdn.jsdelivr.net/gh/highlightjs/cdn-release@10.5.0/build/highlight.min.js"></script>
<!-- and it's easy to individually load additional languages -->
<script src="https://cdn.jsdelivr.net/gh/highlightjs/cdn-release@10.5.0/build/languages/python.min.js"></script>
<script>hljs.initHighlightingOnLoad();</script>

<!-- a bit of JS that allows a modal popup when the first -->
<!-- list element of the navbar (Instructions) is clicked -->
<!-- adapted from: https://github.com/rstudio/flexdashboard/issues/208 -->

<style type="text/css">
#data {
  padding: 5% 5% 5% 5%;
  background-color:#f2f2f2;
}
#methodology {
  padding: 5% 5% 5% 5%;
  background-color:#f2f2f2;
}
#about {
  padding: 5% 5% 5% 5%;
  background-color:#f2f2f2;
}
#instructions {
  padding: 5% 5% 5% 5%;
  background-color:#f2f2f2;
}
</style>


<script>

  $('.navbar-brand').wrap('<a href="http://www.gsawellfailure.com">');
  
  <!-- code to link navbar links to modal popups -->
  <!-- modal popup when navbar list elements are clicked -->
  <!-- $(document).ready(function() { -->
  <!--   $('#dashboard-container').on('flexdashboard:layoutcomplete', -->
  <!--     function() { -->
  <!--       $('#navbar li:nth-child(4)').click(function() { -->
  <!--         $('#md-instructions').modal(); }); -->
  <!--   }) -->
  <!-- }) -->

  <!-- $(document).ready(function() { -->
  <!--   $('#dashboard-container').on('flexdashboard:layoutcomplete',  -->
  <!--     function() { -->
  <!--       $('#navbar li:nth-child(2)').click(function() { -->
  <!--         $('#md-methodology').modal(); }); -->
  <!--   }) -->
  <!-- }) -->

  <!-- $(document).ready(function() { -->
  <!--   $('#dashboard-container').on('flexdashboard:layoutcomplete',  -->
  <!--     function() { -->
  <!--       $('#navbar li:nth-child(3)').click(function() { -->
  <!--         $('#md-data').modal(); }); -->
  <!--   }) -->
  <!-- }) -->

  <!-- $(document).ready(function() { -->
  <!--   $('#dashboard-container').on('flexdashboard:layoutcomplete',  -->
  <!--     function() { -->
  <!--       $('#navbar li:nth-child(4)').click(function() { -->
  <!--         $('#md-about').modal(); }); -->
  <!--   }) -->
  <!-- }) -->
  
  <!-- modal popup when valueBoxes are clicked -->
  $(document).ready(function() {
    $('#dashboard-container').on('flexdashboard:layoutcomplete', 
      function() {
        $('#groundwater-level-decline').click(function() {
          $('#md-groundwater-level-decline').modal(); });
    })
  })
  
  $(document).ready(function() {
    $('#dashboard-container').on('flexdashboard:layoutcomplete', 
      function() {
        $('#well-failure-count').click(function() {
          $('#md-well-failure-count').modal(); });
    })
  })
  
  $(document).ready(function() {
    $('#dashboard-container').on('flexdashboard:layoutcomplete', 
      function() {
        $('#well-failure-percent').click(function() {
          $('#md-well-failure-percent').modal(); });
    })
  })
  
  $(document).ready(function() {
    $('#dashboard-container').on('flexdashboard:layoutcomplete', 
      function() {
        $('#cost-estimate').click(function() {
          $('#md-cost-estimate').modal(); });
    })
  })
  
  $(document).ready(function() {
    $('#dashboard-container').on('flexdashboard:layoutcomplete', 
      function() {
        $('#plot-description').click(function() {
          $('#md-plot-description').modal(); });
    })
  })
  
  $(document).ready(function() {
    $('#dashboard-container').on('flexdashboard:layoutcomplete', 
      function() {
        $('#map-description').click(function() {
          $('#md-map-description').modal(); });
    })
  })
</script>

<!-- Home {.hidden} -->
<!-- =====================================  -->

```{r, echo = FALSE}
library(flexdashboard)
library(shiny)
library(bsplus)
library(leaflet)
library(htmltools)
library(htmlwidgets)
library(plotly)
library(stringr)
library(readr)
library(here)
library(leafem)
library(raster)
library(sf)
# includeMarkdown(here("jamstack", "etc", "home.md"))
```


Map {.hidden}
===================================== 

```{r setup, include=FALSE}
# read current groundwater level, mt surface, gsas, model output
gwl <- read_rds(here("code", "results", "gwl_2019_avg_ll.rds"))
mts <- read_rds(here("code", "results", "mt_surface_cv.rds")) %>% projectRaster(to = gwl)
gwl <- mask(gwl, mts) # mask 2019 values to 2040 raster
gsa <- read_rds(here("code", "results", "gsa_ll.rds"))
l   <- read_rds(here("code", "results", "model_output.rds"))
l   <- l[ params$gsa_names_full ][[1]]$failp
# l   <- l[ "Northern Central" ][[1]]$failp # debugging
# ivs <- read_rds(here("code","results","ivs.rds")) %>%
  # filter(gsp_name == params$selected_gsa)
# filter(gsp_name == "ALL") # debugging
mtfs <- read_rds(here("code", "results", "mt_fail_summary.rds")) %>% 
  filter(gsp_name == params$selected_gsa)
  # filter(gsp_name == "northern_central") # debugging

# active and failing points for leaflet not on main page
if(params$selected_gsa != "ALL"){
  lp <- read_rds(here("code", "results", "results_leaflet.rds")) %>% .[[1]] %>% 
    spTransform(crs(gwl)) %>% 
    st_as_sf() %>% 
    filter(gsp_name == params$gsa_names_full)
    # filter(gsp_name == "Northern Central (DM)")
  lp <- mutate(lp, lat = st_coordinates(lp)[,1], lng = st_coordinates(lp)[,2])
  lp$high_0 <- "active"
}

# store Rmd params as global variables
selected_gsa     <- params$selected_gsa #"ALL" # debugging
selected_gsa_url <- str_replace_all(selected_gsa, "_", "-")
selected_decline <- params$selected_decline #"mt"  # debugging
selected_decline_ft <- ifelse(selected_decline != "mt",
                              paste0(selected_decline, " ft. of decline"),
                              "Minimum Threshold")

# value box data for declines %in% 10 - 300 ft
if(selected_decline != "mt") { 
  vb1 = paste0(selected_decline, " ft.") 
  vbd <- filter(l, decline == selected_decline) %>% 
    mutate(
      vb2 = ifelse(failn_low == failn_high, failn_low, paste0(failn_low, "-", failn_high)),
      vb3 = ifelse(failn_low == failn_high, 
                   formatC(round(failp_low*100,  1), format="f", digits=1),
                   paste0(formatC(round(failp_low*100,  1), format="f", digits=1), "-", 
                   formatC(round(failp_high*100, 1), format="f", digits=1))
                   ),
      vb4 = ifelse(round(cost_low/1e6, 1) == round(cost_high/1e6, 1),
                   formatC(round(cost_low/ 1e6, 1), format="f", digits=1),
                   paste0(formatC(round(cost_low/ 1e6, 1), format="f", digits=1), "-", 
                   formatC(round(cost_high/1e6, 1), format="f", digits=1))
                   )
    )
  vb2 = vbd$vb2
  vb3 = vbd$vb3
  vb4 = paste0("$", vbd$vb4, "M")
}

# value box data for declines == 0 ft 
if(selected_decline == 0) { 
  vb2 = "0 ft."
  vb2 = "0"
  vb3 = "0" 
  vb4 = "$0" 
}

# value box data for declines == mt
if(selected_decline == "mt") { 
  vb1 = "Min threshold" 
  vbd_low = mtfs %>% 
    mutate(
      vb2 = low,
      vb3 = formatC(round(failp_low*100,  1), format="f", digits=1),
      vb4 = formatC(round(cost_low/ 1e6,  1), format="f", digits=1)
    ) %>% 
    dplyr::select(vb2:vb4)
  vbd_high = mtfs %>% 
    mutate(
      vb2 = high,
      vb3 = formatC(round(failp_high*100,  1), format="f", digits=1),
      vb4 = formatC(round(cost_high/ 1e6,  1), format="f", digits=1)
    ) %>% 
    dplyr::select(vb2:vb4)
  vb2 = ifelse(vbd_low$vb2 == vbd_high$vb2,
               vbd_low$vb2,
               paste0(vbd_low$vb2, "-", vbd_high$vb2))
  vb3 = ifelse(vbd_low$vb2 == vbd_high$vb2,
               vbd_low$vb3,
               paste0(vbd_low$vb3, "-", vbd_high$vb3))
  vb4 = ifelse(vbd_low$vb4 == vbd_high$vb4,
               vbd_low$vb4,
               paste0("$", vbd_low$vb4, "-", vbd_high$vb4, "M"))
}

# gsa names
gsa_names <- gsa@data$gsp_name %>% 
  tolower() %>% 
  str_remove_all("[\\(\\)]") %>% 
  str_remove_all(" dm") %>% 
  str_replace_all(" |-", "_") 

# filter gsa polygons to selected_gsa
if(selected_gsa != "ALL") {
  gsa <- gsa[which(gsa_names == selected_gsa), ]
}

# utility functions
source(here("jamstack", "etc", "functions.R"))
  
# root url for links
root <- "https://www.gsawellfailure.com/gsas/"
```


<i class="fas fa-exclamation-circle"></i> Mobile view detected {.sidebar data-width=150 data-padding=10}
-----------------------------------------------------------------------

```{r sidebar downdown menus}
# GSA dropdown
tags$div(
  class="dropdown", id = "content-desktop",
  tags$button(
    class="dropbtn", "Select a GSA"),
  tags$div(
    class = "dropdown-content",
    tags$a(href = paste0(root, "ALL/", selected_decline), "ALL"),
    # tags$a(href = paste0(root, "aliso/", selected_decline), "Aliso (DM)"),
    # tags$a(href = paste0(root, "alpaugh-tule/", selected_decline), "Alpaugh (Tule)"),
    tags$a(href = paste0(root, "buena-vista-kern/", selected_decline), "Buena Vista (Kern)"),
    tags$a(href = paste0(root, "central-kings/", selected_decline), "Central Kings"),
    tags$a(href = paste0(root, "chowchilla/", selected_decline), "Chowchilla"),
    # tags$a(href = paste0(root, "delano-earlimart-tule/", selected_decline), "Delano-Earlimart (Tule)"),
    tags$a(href = paste0(root, "east-kaweah/", selected_decline), "East Kaweah"),
    tags$a(href = paste0(root, "east-tule/", selected_decline), "East Tule"),
    tags$a(href = paste0(root, "eastern-san-joaquin/", selected_decline), "Eastern San Joaquin"),
    # tags$a(href = paste0(root, "farmers/", selected_decline), "Farmers (DM)"),
    # tags$a(href = paste0(root, "fresno-county/", selected_decline), "Fresno County (DM)"),
    tags$a(href = paste0(root, "grassland/", selected_decline), "Grassland (DM)"),
    # tags$a(href = paste0(root, "gravelly-ford-madera/", selected_decline), "Gravelly Ford (Madera)"),
    tags$a(href = paste0(root, "greater-kaweah/", selected_decline), "Greater Kaweah"),
    # tags$a(href = paste0(root, "henry-miller-kern/", selected_decline), "Henry Miller (Kern)"),
    tags$a(href = paste0(root, "james-kings/", selected_decline), "James (Kings)"),
    tags$a(href = paste0(root, "kern-groundwater-authority/", selected_decline), "Kern Groundwater Authority"),
    tags$a(href = paste0(root, "kern-river/", selected_decline), "Kern River"),
    tags$a(href = paste0(root, "kings-river-east/", selected_decline), "Kings River East"),
    tags$a(href = paste0(root, "lower-tule-river/", selected_decline), "Lower Tule River"),
    tags$a(href = paste0(root, "madera-joint/", selected_decline), "Madera Joint"),
    tags$a(href = paste0(root, "mc-mullin/", selected_decline), "Mc Mullin"),
    tags$a(href = paste0(root, "merced/", selected_decline), "Merced"),
    tags$a(href = paste0(root, "mid-kaweah/", selected_decline), "Mid Kaweah"),
    # tags$a(href = paste0(root, "new-stone-madera/", selected_decline), "New Stone (Madera)"),
    tags$a(href = paste0(root, "north-fork-kings/", selected_decline), "North Fork Kings"),
    tags$a(href = paste0(root, "north-kings/", selected_decline), "North Kings"),
    tags$a(href = paste0(root, "northern-central/", selected_decline), "Northern Central (DM)"),
    tags$a(href = paste0(root, "pixley-tule/", selected_decline), "Pixley (Tule)"),
    # tags$a(href = paste0(root, "root-creek-madera/", selected_decline), "Root Creek (Madera)"),
    tags$a(href = paste0(root, "sjrec/", selected_decline), "SJREC (DM)"),
    tags$a(href = paste0(root, "south-kings/", selected_decline), "South Kings"),
    # tags$a(href = paste0(root, "tri-county-tule/", selected_decline), "Tri-County (Tule)"),
    tags$a(href = paste0(root, "tulare-lake/", selected_decline), "Tulare Lake"),
    tags$a(href = paste0(root, "westside/", selected_decline), "Westside")
    )
)

tags$br()
tags$br()

# groundwater level dropdown
tags$div(
  class="dropdown", id = "content-desktop",
  tags$button(
    class="dropbtn", paste0("Select a groundwater scenario")),
  tags$div(
    class = "dropdown-content",
    tags$a(href = paste0(root, selected_gsa_url, "/", "mt"),  "Minimum Threshold"),
    tags$a(href = paste0(root, selected_gsa_url, "/", "0"),   "0 ft decline"),
    tags$a(href = paste0(root, selected_gsa_url, "/", "10"),  "10 ft decline"),
    tags$a(href = paste0(root, selected_gsa_url, "/", "20"),  "20 ft decline"),
    tags$a(href = paste0(root, selected_gsa_url, "/", "30"),  "30 ft decline"),
    tags$a(href = paste0(root, selected_gsa_url, "/", "40"),  "40 ft decline"),
    tags$a(href = paste0(root, selected_gsa_url, "/", "50"),  "50 ft decline"),
    tags$a(href = paste0(root, selected_gsa_url, "/", "100"), "100 ft decline"),
    tags$a(href = paste0(root, selected_gsa_url, "/", "150"), "150 ft decline"),
    tags$a(href = paste0(root, selected_gsa_url, "/", "200"), "200 ft decline"),
    tags$a(href = paste0(root, selected_gsa_url, "/", "250"), "250 ft decline"),
    tags$a(href = paste0(root, selected_gsa_url, "/", "300"), "300 ft decline")
    )
)

# mobile only message
tags$div(
  id = "content-mobile",
  tags$p("The data visualizations on this website are too large for mobile devices and small screens. For best results, please visit gsawellfailure.com on a PC.")
)

tags$br()
tags$br()
```


<!-- Row {data-width=100} -->
Row
-----------------------------------------------------------------------

```{r}
# markdown files for methods behind each of the reported statistics, obtained when clicking value boxes
# bs_modal(
#   id = "md-instructions",
#   title = htmltools::HTML('<h1>How to use this website</h1>'),
#   body = includeMarkdown(here("jamstack", "etc", "instructions.md")),
#   size = "large"
# )
# bs_modal(
#   id = "md-methodology",
#   title = htmltools::HTML('<h1>Science and methodology</h1>'),
#   body = includeMarkdown(here("jamstack", "etc", "methodology.md")),
#   size = "large"
# )
# bs_modal(
#   id = "md-data",
#   title = htmltools::HTML('<h1>Data access</h1>'),
#   body = includeMarkdown(here("jamstack", "etc", "data.md")),
#   size = "large"
# )
# bs_modal(
#   id = "md-about",
#   title = htmltools::HTML('<h1>About</h1>'),
#   body = includeMarkdown(here("jamstack", "etc", "about.md")),
#   size = "large"
# )
bs_modal(
  id = "md-groundwater-level-decline",
  title = htmltools::HTML('<h1 style="color:cornflowerblue"><i class="fas fa-arrow-down"></i> Groundwater level decline</h1>'),
  body = includeMarkdown(here("jamstack", "etc", "groundwater_level_decline.md")),
  size = "large"
)
bs_modal(
  id = "md-well-failure-count",
  title = htmltools::HTML('<h1 style="color:#fb4f73"><i class="fas fa-times-circle"></i> Well failure count</h1>'),
  body = includeMarkdown(here("jamstack", "etc", "well_failure_count.md")), 
  size = "large"
)
bs_modal(
  id = "md-well-failure-percent",
  title = htmltools::HTML('<h1 style="color:sandybrown"><i class="fas fa-percent"></i> Well failure percent</h1>'),
  body = includeMarkdown(here("jamstack", "etc", "well_failure_percent.md")),
  size = "large"
)
bs_modal(
  id = "md-cost-estimate",
  title = htmltools::HTML('<h1 style="color:darkseagreen"><i class="fas fa-money-check-alt"></i> Cost estimate</h1>'),
  body = includeMarkdown(here("jamstack", "etc", "cost_estimate.md")),
  size = "large"
)
bs_modal(
  id = "md-plot-description",
  title = htmltools::HTML('<h1 style="color:grey"><i class="fas fa-question-circle"></i> Forecasted percentage of dry wells</h1>'),
  body = includeMarkdown(here("jamstack", "etc", "plot_description.md")),
  size = "large"
)
bs_modal(
  id = "md-map-description",
  title = htmltools::HTML('<h1 style="color:grey"><i class="fas fa-question-circle"></i> Critical priority GSAs and groundwater levels</h1>'),
  body = includeMarkdown(here("jamstack", "etc", "map_description.md")),
  size = "large"
)
```

```{r, include=FALSE}
# continuation of the above
# bs_button("Click for modal", button_type = "primary") %>%
#   bs_attach_modal("md-instructions")
# bs_button("Click for modal", button_type = "primary") %>%
#   bs_attach_modal("md-methodology")
# bs_button("Click for modal", button_type = "primary") %>%
#   bs_attach_modal("md-data")
# bs_button("Click for modal", button_type = "primary") %>%
#   bs_attach_modal("md-about")
bs_button("Click for modal", button_type = "primary") %>%
  bs_attach_modal("md-groundwater-level-decline")
bs_button("Click for modal", button_type = "primary") %>%
  bs_attach_modal("md-well-failure-count")
bs_button("Click for modal", button_type = "primary") %>%
  bs_attach_modal("md-well-failure-percent")
bs_button("Click for modal", button_type = "primary") %>%
  bs_attach_modal("md-cost-estimate")
bs_button("Click for modal", button_type = "primary") %>%
  bs_attach_modal("md-plot-description")
bs_button("Click for modal", button_type = "primary") %>%
  bs_attach_modal("md-map-description")
# bs_button("How to use this website", button_type = "info") %>%
#   bs_attach_modal("md-instructions")
```


### Groundwater level decline
```{r}
valueBox(vb1,
         color = "primary",
         icon = "ion-arrow-down-a")
         # icon = "fa-arrow-down")
```

### Well failure count
```{r}
valueBox(vb2,
         color = "danger", 
         icon = "fa-times-circle")
```

### Well failure percent
```{r}
valueBox(vb3,
         color = "warning", 
         icon = "fa-percent")
```

### Cost estimate
```{r}
valueBox(vb4,
         color = "success", 
         icon = "ion-cash")
         # icon = "fa-money-check-alt")
```



Row
-----------------------------------------------------------------------

### `r ifelse(selected_gsa != "ALL", paste0("<font size='+1.5'><button type='button' style='border:none; background-color: Transparent;' data-toggle='modal' data-target='#md-map-description'><i class='fas fa-question-circle'></i></button> ", gsa@data$gsp_name, " GSA and groundwater levels</font>"), "<font size='+1.5'><button type='button' style='border:none; background-color: Transparent;' data-toggle='modal' data-target='#md-map-description'><i class='fas fa-question-circle'></i></button> All critical priority GSAs and groundwater levels</font>")`
```{r, leaflet}
leaf_map <- leaflet() %>% addProviderTiles("CartoDB")

# color palettes for gwl decline
# col <- rev(colormap::colormap(colormap::colormaps$magma, nshades = 100))
col <- rev(colormap::colormap(colormap::colormaps$portland, reverse=TRUE, nshades = 50))
# hack the color pal to include values in both scales (use -10)
pal <- colorNumeric(col, c(-10,raster::values(mts)), na.color = "transparent")

# read all plotly plots in
if(selected_gsa == "ALL") {
  pop <- vector("list", length(gsa_names))
  for(i in 1:length(gsa_names)){
    pop[[i]] <- 
      read_rds(
        paste0("~/Documents/Github/aife/plotly/",
               selected_decline,"_", gsa_names[i], ".rds"
        )
      ) %>% 
      as.tags() %>%
      {tags$div(style="width:270px; height:220px;", .)} %>%
      as.character() %>% 
      stringr::str_replace("height:400px","height:100%")
    pop[[i]] <- 
      paste0("<center><em><b><font size='+1'>", 
             tags$a(gsa@data$gsp_name[i], 
                    href = 
                      paste0(root, 
                             str_replace_all(gsa_names[i],"_","-"),
                                             "/", selected_decline)
                    ),
             "</font></b></em></center>",
             pop[[i]]
      )
  }
}

# remove popups for individual GSAs
if(selected_gsa != "ALL") { pop <- NULL}

# setZoom parameters
xy        <- sp::bbox(gsa) %>% apply(1, mean)
names(xy) <- NULL
xy        <- xy + c(0.4, 0.2)
zoom      <- ifelse(selected_gsa == "ALL", 7, 8)

# overlayGroups label depends on the selected_gsa
if(selected_gsa == "ALL"){og <- "critical priority GSAs"}
if(selected_gsa != "ALL"){og <- params$gsa_names_full}

# show active and failing wells on non-main page
if(selected_gsa != "ALL"){
  og <- c(og, "domestic wells")
  pal_fail <- colorFactor(c("navy", "red"), domain = c("active", "failing"))
  
  # add active and failing wells in separate layers 
  # lpa <- lp[st_drop_geometry(lp)[ , paste0("high_", 100)] == "active", ]
  # lpf <- lp[st_drop_geometry(lp)[ , paste0("high_", 100)] == "failing", ]
  
  leaf_map <- leaf_map %>%
    addMapPane("apts", zIndex = 430) %>%
    # addMapPane("fpts", zIndex = 420) %>%
    addMapPane("gsap", zIndex = 410) %>%
    # active
    addCircleMarkers(lng = lp$lat, lat = lp$lng,
    color = pal_fail(dplyr::pull(lp, paste0("high_", selected_decline))),
    group = og[2],
    options = pathOptions(pane = "apts"),
    clusterOptions = markerClusterOptions(),
    stroke = FALSE, fillOpacity = 0.5, radius = 8,
    popup = glue::glue("<b>WCR Number:</b> {lp$WCRNumber}<br>
                       <b>Estimated pump location:</b> {round(lp$mean_ci_lower,2)}-{round(lp$mean_ci_upper,2)} ft BLS<br>
                       <b>Total completed depth:</b> {round(lp$TotalCompletedDepth,2)} ft BLS")
    ) %>% 

    # gsa polygon
    addPolygons(data = gsa, weight = 1, opacity = 1, fillOpacity = 0.1,
                group = og[1], # gsa name
                label = ~gsp_name, 
                color = "black",
                options = pathOptions(pane = "gsap"),
                highlightOptions = 
                  highlightOptions(color = "white", weight = 2,
                                   bringToFront = TRUE),
                labelOptions = labelOptions(textsize = "13px"),
                popup = pop
    ) %>% 
    # groundwater level
    addRasterImage(mts, opacity = 0.8, colors = pal, 
                   layerId = "2040", group = "minimum threshold") %>%
    addRasterImage(gwl, opacity = 0.8, colors = pal, 
                   layerId = "2019", group = "2019 groundwater level") %>%
    addLegend(pal = pal, values = raster::values(mts),
              title    = "Groundwater <br>level (ft. BLS)",
              position = "bottomright") %>%
    
    # layer control
    addLayersControl(
      overlayGroups = rev(og),
      baseGroups    = c("minimum threshold", "2019 groundwater level"),
      options       = layersControlOptions(collapsed = FALSE,
                                           position = "bottomleft")
    ) %>%
    
    # center
    # setView(-119.7, 36.8, 7) %>% 
    setView(xy[1], xy[2], zoom) %>% 
    
    # zoom to center
    addEasyButton(easyButton(
      icon="fa-globe", title="Zoom to center",
      onClick=JS(
        paste0("function(btn, map){ map.setView([",
               xy[2], ",", xy[1], "],", zoom, ")",
               "; }")
        ),
      position = "topleft")
    ) %>% 
    
    # full screen
    leaflet.extras::addFullscreenControl(position = "topleft") %>% 
  
    # raster value display
    leafem::addMouseCoordinates() %>%
      onRender("
          function() {
              $('.leaflet-control-layers-list').prepend('<label style=\"text-align:center\">TOGGLE OPTIONS<hr></label>');
          }
      ") %>% 
    # leafem::addImageQuery(gwl, layerId = "2019",
    #                       group = "2019 groundwater level", prefix = "",
    #                       digits = 2, position = "bottomright") %>%
    # leafem::addImageQuery(mts, layerId = "2040",
    #                       group = "2040 min threshold", prefix = "",
    #                       digits = 2, position = "bottomright") %>%
    
    # JS for polygon popups
    onRender(
      "function(el,x) {
      this.on('popupopen', function() {HTMLWidgets.staticRender(); remove()})
      }"
    ) %>%
    add_deps("plotly") %>%
    htmltools::attachDependencies(plotly:::plotlyMainBundle(), append = TRUE) %>%
    htmltools::attachDependencies(crosstalk::crosstalkLibs(),  append = TRUE) %>%
    browsable()
}

# map 
if(selected_gsa == "ALL"){
    
  leaf_map <- leaf_map %>% 
    # groundwater level
    addRasterImage(mts, opacity = 0.8, colors = pal, 
                   layerId = "2040", group = "minimum threshold") %>%
    addRasterImage(gwl, opacity = 0.8, colors = pal, 
                   layerId = "2019", group = "2019 groundwater level") %>%
    addLegend(pal = pal, values = raster::values(mts),
              title    = "Groundwater <br>level (ft. BLS)",
              position = "bottomright") %>%
    
    # layer control
    addLayersControl(
      overlayGroups = rev(og),
      baseGroups    = c("minimum threshold", "2019 groundwater level"),
      options       = layersControlOptions(collapsed = FALSE,
                                           position = "bottomleft")
    ) %>%
    
    # center
    # setView(-119.7, 36.8, 7) %>% 
    setView(xy[1], xy[2], zoom) %>% 
    
    # zoom to center
    addEasyButton(easyButton(
      icon="fa-globe", title="Zoom to center",
      onClick=JS(
        paste0("function(btn, map){ map.setView([",
               xy[2], ",", xy[1], "],", zoom, ")",
               "; }")
        ),
      position = "topleft")
    ) %>% 
    
    # full screen
    leaflet.extras::addFullscreenControl(position = "topleft") %>% 
  
    # polygons
    addPolygons(data = gsa, weight = 1, opacity = 1, fillOpacity = 0.1,
                group = og[1], # gsa name
                label = ~gsp_name, 
                color = "black",
                highlightOptions = 
                  highlightOptions(color = "white", weight = 2,
                                   bringToFront = TRUE),
                labelOptions = labelOptions(textsize = "13px"),
                popup = pop
    ) %>% 
    
    # raster value display
    leafem::addMouseCoordinates() %>%
      onRender("
          function() {
              $('.leaflet-control-layers-list').prepend('<label style=\"text-align:center\">TOGGLE OPTIONS<hr></label>');
          }
      ") %>% 
    # leafem::addImageQuery(gwl, layerId = "2019",
    #                       group = "2019 groundwater level", prefix = "",
    #                       digits = 2, position = "bottomright") %>%
    # leafem::addImageQuery(mts, layerId = "2040",
    #                       group = "2040 min threshold", prefix = "",
    #                       digits = 2, position = "bottomright") %>%
    
    # JS for polygon popups
    onRender(
      "function(el,x) {
      this.on('popupopen', function() {HTMLWidgets.staticRender(); remove()})
      }"
    ) %>%
    add_deps("plotly") %>%
    htmltools::attachDependencies(plotly:::plotlyMainBundle(), append = TRUE) %>%
    htmltools::attachDependencies(crosstalk::crosstalkLibs(),  append = TRUE) %>%
    browsable()
}

# show map
leaf_map
```

### `r ifelse(selected_gsa != "ALL", paste0("<font size='+1.5'><button type='button' style='border:none; background-color: Transparent;' data-toggle='modal' data-target='#md-plot-description'><i class='fas fa-question-circle'></i></button> Forecasted percentage of dry wells for ", gsa@data$gsp_name, " GSA</font>"), "<font size='+1.5'><button type='button' style='border:none; background-color: Transparent;' data-toggle='modal' data-target='#md-plot-description'><i class='fas fa-question-circle'></i></button> Forecasted percentage of dry wells for all critical priority GSAs</font>")`
```{r, plot}
readr::read_rds(paste0("../plotly/", selected_decline, "_", selected_gsa, ".rds"))
```



Methodology {.hidden}
===================================== 
```{r}
includeMarkdown(here("jamstack", "etc", "methodology.md"))
```

Data {.hidden}
===================================== 
```{r}
includeMarkdown(here("jamstack", "etc", "data.md"))
```

Terms {.hidden}
===================================== 
```{r}
includeMarkdown(here("jamstack", "etc", "terms.md"))
```

Instructions {.hidden}
===================================== 
```{r}
includeMarkdown(here("jamstack", "etc", "instructions.md"))
```

