---
title: "GSA #1"
output: html_document
runtime: shiny_prerendered
---


```{r, include=FALSE}
library(knitr)
knitr::opts_chunk$set(message = FALSE, error = FALSE, warning = FALSE, echo = FALSE)
```


```{r}
library(crosstalk)
library(leaflet)
library(plotly)
library(DT)
library(tidyverse)
library(summarywidget) #devtools::install_github("kent37/summarywidget")
```


```{r}
priority <- "HIGH" # get from params or filter from df of GSA & priority
  
if(priority == "HIGH") 
  pristr <- paste0(" ", fontawesome::fa("exclamation-circle", fill = "red"), 
                   paste0(" Basin prioritization: **<font color = 'red'>", priority, "</font>**") )
if(priority == "MEDIUM") 
  pristr <- paste0(" ", fontawesome::fa("exclamation-circle", fill = "orange"), 
                   paste0(" Basin prioritization: **<font color = 'orange'>", priority, "</font>**") )
if(priority == "LOW") 
  pristr <- paste0(" ", fontawesome::fa("check-circle", fill = "green"), 
                   paste0(" Basin prioritization: **<font color = 'green'>", priority, "</font>**") )

```

## `r pristr`


<div class="alert alert-info alert-dismissible fade in">
  <a href="#" class="close" data-dismiss="alert" aria-label="close">&times;</a>
  <strong>Instructions:</strong> Drag the slider bar below from left to right to select a range of groundwater level decline. Remaining active wells at the specified groundwater level decline are shown in the map and table.
</div>




```{r}
eqs <- highlight_key(quakes)

decline <- filter_slider(
  "depth", "Groundwater level decline (ft)", 
  eqs, ~depth,
  dragRange = TRUE,
  post = " ft"
)
```


```{r}
p <- plot_ly(eqs, x = ~depth, y = ~mag) %>% 
  add_markers(alpha = 0.5) %>% 
  highlight("plotly_selected")

map <- leaflet(eqs) %>% 
  addTiles() %>% 
  addCircles(label = ~depth)

dtab <- datatable(eqs, extensions="Scroller", style="bootstrap", class="compact", width="100%",
    options=list(deferRender=TRUE, scrollY=300, scroller=TRUE))

bscols(
  widths = 12,
  decline
)
```


Given the specified amount of groundwater level decline, an average of `r summarywidget(eqs)` of `r nrow(quakes)` domestic wells in this GSA are expected to remain active.


## Active domestic wells

```{r}
bscols(map, dtab)
```

# Impact summary

```{r}
sigmoid = function(x) {
   1 / (1 + exp(-x))
}

p <- tibble(gwl = seq(0,10, 0.5), 
       n   = sigmoid(round(seq(-5,5, 0.5),0))) %>% 
  mutate(lab = glue::glue("<b>GWL decline (ft):</b> {gwl} <br>",
                          "<b>n failures:</b> {round(n,0)} <br>",
                          "<b>Estimated Cost:</b> ${round(5*n,2)}")) %>% 
  ggplot(aes(gwl, n, text= lab)) +
  geom_point() +
  labs(x = "Uniform groundwater level decline from current conditions",
       y = "Estimated number of well failures")

bscols(widths = 12,
       ggplotly(p, tooltip = "lab"))
```

